---
title: "Codebook"
author: "Cyril Medabalimi"
date: "August 23, 2015"
output: html_document:
  keep_md: true
---

Codebook
========

Variable list and descriptions
------------------------------

Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.
activity         | Activity name
featDomain       | Feature: Time domain signal or frequency domain signal (Time or Freq)
featInstrument   | Feature: Measuring instrument (Accelerometer or Gyroscope)
featAcceleration | Feature: Acceleration signal (Body or Gravity)
featVariable     | Feature: Variable (Mean or SD)
featJerk         | Feature: Jerk signal
featMagnitude    | Feature: Magnitude of the signals calculated using the Euclidean norm
featAxis         | Feature: 3-axial signals in the X, Y and Z directions (X, Y, or Z)
featCount        | Feature: Count of data points used to compute `average`
featAverage      | Feature: Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(Data2)
```


Show a few rows of the dataset
------------------------------

```{r}
head(Data2)
```

Summary of variables
--------------------

```{r}
summary(Data2)
```

Save to file
------------

Save data table objects to a tab-delimited text file called `TidyDataSet.txt`.

```{r save}
write.table(Data2, file = "TidyDataSet.txt",row.name=FALSE)
```


